---
title: "Homework 1"
author: "Ying Jin"
date: "2020/9/15"
output: github_document
---

This is the first homework of P8105.

```{r setup,include = FALSE}
library(tidyverse)
library(ggplot2)
```

## Problem 1

First I create a data frame:

```{r df_create}
prob1_df <- tibble(
  norm_samp = rnorm(10),
  samp_gt_0 = norm_samp > 0,
  char_vec = c('a','b','c','d','e','f','g','h','i','g'),
  factor_vec = factor(c('l','l','s','m','m','s','l','s','m','l'))
)
```

Then I take the `mean` of each variable in the data frame:

```{r df_mean}
mean(prob1_df$norm_samp)
mean(prob1_df$samp_gt_0)
mean(prob1_df$char_vec)
mean(prob1_df$factor_vec)
```

According to the outcome above, `mean` function works on **numeric** and **logical** variables, but doesn't work on **character** and **factor** variables. 

Next I apply `as.numeric` function to the **logical**,**character** and **factor** variables:

```{r as_numeric,eval = FALSE}
as.numeric(prob1_df$samp_gt_0)
as.numeric(prob1_df$char_vec)
as.numeric(prob1_df$factor_vec)
```

According to the results which are not shown here, **logical** and **factor** variables can be converted into numeric, while **character** variable can not. I think that's  because **logical** and **factor** values are stored as integers rather than characters in computer. In this way, the reason why `mean` function works on **logical** variable but not on **character** variable is clear. However, it can't help to explain why I can't get mean of the factor variable by applying `mean` function.

At last, I do some conversation and multiplication on these variables:

```{r convert_multiply}
as.numeric(prob1_df$samp_gt_0)*prob1_df$norm_samp
as.factor(prob1_df$samp_gt_0)*prob1_df$norm_samp
as.numeric(as.factor(prob1_df$samp_gt_0))*prob1_df$norm_samp
```

## Problem 2

First I load the `penguins` dataset:

```{r load_data}
data("penguins", package = "palmerpenguins")
```

* Brief Description of `penguins`
  * It includes the species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g,sex and year.
    * Species include Adelie, Gentoo and Chinstrap.
    * Islands include Torgersen, Biscoe and Dream
    * Sex is male  or female or NA 
    * Years include 2007,2008 and 2009
  * It has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
  * The mean flipper length is `r round(mean(pull(penguins,flipper_length_mm),na.rm = TRUE),digits = 2)`.
  
Then I make a scatter plot of `flipper_length_mm` vs `bill_length_mm, with `species` as color points:

```{r}
ggplot(penguins,aes(x = bill_length_mm,y = flipper_length_mm,color = species)) + geom_point()
```

