---
title: "p8105_hw1_yj2622"
author: "Ying Jin"
date: "2020/9/15"
output: github_document
---

This is the first homework of P8105!

# Problem 1

```{r setup,include = FALSE}
library(tidyverse)
```

First I create a data frame:

```{r df_create}
df_1 <- tibble(
  norm_samp = rnorm(10),
  logical = norm_samp > 0,
  char = c('a','b','c','d','e',
           'f','g','h','i','g'),
  factor = factor(c('l','l','s','m',
                    'm','s','l','s','m','l'))
)
```

Then I take the `mean` of each variable in the data frame:

```{r df_mean}
mean(df_1$norm_samp)
mean(df_1$logical)
mean(df_1$char)
mean(df_1$factor)
```

According to the outcome above, `mean` function works on **numeric** and **logical** variables, but doesn't work on **character** and **factor** variables. 

Next I apply `as.numeric` function to the **logical**,**character** and **factor** variables:

```{r as_numeric,eval = FALSE}
as.numeric(df_1$logical)
as.numeric(df_1$char)
as.numeric(df_1$factor)
```

According to the results which are not shown here, **logical** and **factor** variables can be converted into numeric, while **character** variable can not. I think that's  because **logical** and **factor** values are stored as integers rather than characters in computer. In this way, the reason why `mean` function works on **logical** variable but not on **character** variable is clear. However, it can't help to explain why I can't get mean of the factor variable by applying `mean` function.